---
title: "Getting Start With Binomial Package"
author: "Yunzhe Zhou"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```


## Binomial

The package "binomial" is an implementation for calculate the binomial probability and related measures, which also visualizes the related distribution and culmulative distriburion.


## Calculate some basic measures

Calculate E(X) given X is B(n,p)

```{r}
expectation=bin_mean(trials=5,prob=0.3)
expectation
```

Calculate Var(X) given X is B(n,p)

```{r}
variance=bin_variance(trials=5,prob=0.3)
variance
```

Calculate mode of X given X is B(n,p)

```{r}
mode=bin_mode(trials=5,prob=0.3)
mode
```

Calculate skewness of X given X is B(n,p)

```{r}
skewness=bin_skewness(trials=5,prob=0.3)
skewness
```

Calculate kurtosis of X given X is B(n,p)

```{r}
kurtosis=bin_skewness(trials=5,prob=0.3)
kurtosis
```


Calculate $\binom n k$

```{r}
choose <- bin_choose(n = 10, k = 3)
choose
```


Calculate the probability when X=k for binomial distribution

```{r}
probability=bin_probability(success=3,trials=5,prob=0.3)
probability
```


## Create an object of class "binvar"

```{r}
object=bin_variable(trials=5,prob=0.3)
object
```

## Show the summary of the binomial distribution

```{r}
summary(object)
```


## Show the table of the binomial distribution

Show the table of distribution

```{r}
dist1=bin_distribution(trials=5,prob=0.3)
dist1
```


Show the table of the cumulative distribution

```{r}
dist2=bin_cumulative(trials=5,prob=0.3)
dist2
```

## Show the plot of the binomial distribution

show the plot of the disribution

```{r}
plot(dist1)
```

show the plot of the cumulative distribution

```{r}
plot(dist2)
```


